---
title: "Workshop Attendees"
subtitle: "Produce Roster for printing via Excel ; Visualize Attendance"
output: 
  html_document:
    fig_width: 10
    fig_height: 7
    fig_caption: true
    dev: "svg"
date: "`r Sys.Date()`"
params:
  upload_googlesheets: FALSE 
  generate_images: FALSE
  generate_email_subscribers: FALSE
  generate_print_roster: FALSE
---

## How to Run


To generate a workshop roster (CSV), email addresses to be added to marketing systems, and images visualizing registrants by group

- From Windows-Explorer, double-click update_attendance.Rmd ; pick an attendance file
- Look in the output directory for reports

To upload the attendance data into Google Drive

- From Windows-Explorer, double-click update_attendance.Rmd ; pick an attendance file
- Look in your Google Drive home directory ; manually move to the CDVS workshop attendance folder for the proper year



## Libraries, packages, set-up, ingest data, wrangle.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(hrbrthemes)
library(googlesheets4)
library(fs)
library(gt)
```

```{r}

registered_df <- tibble(path_rel(choose.files())) %>% 
  rename(filepath = 1)
registered_df <- registered_df %>% 
  mutate(registration_status = case_when(
    str_detect(filepath, "attendees") ~ "Registered",
    str_detect(filepath, "wait_list") ~ "Waitlist"
  )) %>% 
  mutate(wid = str_extract(filepath, "(?<=(attendees|list)_)\\d+(?=_\\d+)"))

my_df <- read_csv(registered_df$filepath[1], skip = 9)

workshop_metadata <- read_csv(registered_df$filepath, col_names = FALSE, n_max = 7) %>% 
  separate(X1, into = c("var", "val") , sep = ",", extra = "merge") %>% 
  mutate(val = str_remove_all(val, '"'))

workshop_title <- workshop_metadata %>% 
  filter(var == "Event") %>% 
  pull(val)

workshop_date <- workshop_metadata %>% 
  filter(var == "Date & Time") %>% 
  separate(val, into = c("time", "day", "month_day", "year"), sep = ",") %>% 
  unite("date", month_day:year, sep = ", ") %>% 
  mutate(date = str_trim(date)) %>% 
  mutate(date = clock::date_parse(date, format = "%B %d, %Y"))

my_df <- my_df %>% 
  janitor::clean_names() 
my_df <- my_df %>% 
  filter(str_detect(x2_academic_status_or_other, regex("graduate|staff|post|faculty|other", ignore_case = TRUE))) %>% 
  mutate(registration_status = registered_df$registration_status[1])
```

```{r}
attendance_headers <- read_csv("config/cdvs_workshop_attendance_headers.csv")
```

```{r}
dir_create("output/attendance_upload")
dir_create("output/email_subscriptions")
dir_create("output/images")
```


## Reports & Viz

### Academic status


```{r}
my_df %>% 
  count(x2_academic_status_or_other, sort = TRUE) %>% 
  gt()
```

### Departmental affiliations

```{r}
my_df %>% 
  # group_by(x2_academic_status_or_other) %>% 
  count(x3_discipline_or_affiliation, sort = TRUE) %>% 
  gt()
```
```{r figure: attendance by discipline, fig.height=6, fig.width=10, message=FALSE, warning=FALSE}
my_df %>% 
  mutate(x3_discipline_or_affiliation = fct_rev(fct_infreq(x3_discipline_or_affiliation))) %>% 
  mutate(x3_discipline_or_affiliation = fct_lump_min(x3_discipline_or_affiliation, 3, other_level = "Other / None")) %>% 
  ggplot(aes(x3_discipline_or_affiliation, fill = fct_rev(fct_infreq(x2_academic_status_or_other)))) +
  geom_bar() +
  scale_x_discrete(label=function(x) abbreviate(x, minlength=10, method = "both.sides", use.classes = TRUE)) +
  coord_flip() +
  scale_fill_ipsum() +
  theme_ipsum(grid = "X") +
  theme(plot.title.position = "plot") +
  labs(fill = "Academic status", x = "", y = "",
       title = "Attendance by Discipline",
       subtitle = str_glue("{workshop_title}"),
       caption = "Source: CDVS Workshop Registration") + 
  guides(fill = guide_legend(reverse=TRUE))
```


```{r save figure: attendance by discipline, evale=params$generate_images}
ggsave(str_glue("output/images/",  "who_we_are_", 
                {as.character(workshop_date %>% pull(date))}, 
                "_", {Sys.getpid()}, ".svg"), 
       device = "svg", width = 10, height = 6)
```

```{r figure: facetwrap attendance by discipline, fig.height=6, fig.width=10, message=FALSE, warning=FALSE}
my_df %>% 
  mutate(x3_discipline_or_affiliation = fct_rev(fct_infreq(x3_discipline_or_affiliation))) %>% 
  mutate(x3_discipline_or_affiliation = fct_lump_min(x3_discipline_or_affiliation, 3, other_level = "Other / None")) %>% 
  ggplot(aes(x3_discipline_or_affiliation, fill = fct_rev(fct_infreq(x3_discipline_or_affiliation)))) +
  geom_bar(show.legend = FALSE) +
  scale_x_discrete(label=function(x) abbreviate(x, minlength=10, method = "both.sides", use.classes = TRUE)) +
  coord_flip() +
  scale_fill_ipsum() +
  facet_wrap(~ fct_infreq(x2_academic_status_or_other)) +
  theme_ipsum(grid = "X") +
  theme(plot.title.position = "plot") +
  labs(fill = "Academic status", x = "", y = "",
       title = "Attendance by Discipline",
       subtitle = str_glue("{workshop_title}"),
       caption = "Source: CDVS Workshop Registration") + 
  guides(fill = guide_legend(reverse=TRUE))


```


```{r save figure: facetwrap attendance by discipline, evale=params$generate_images}
ggsave(str_glue("output/images/",  "who_we_are_facetwrap_", 
                {as.character(workshop_date %>% pull(date))}, 
                "_", {Sys.getpid()}, ".svg"), 
       device = "svg", width = 10, height = 6)
```

### Duke Affiliation?

```{r}
# glimpse(my_df)
my_df %>% 
  count(x1_are_you_affiliated_with_duke_university_duke_medical_center_dcri_or_another_duke_group, sort = TRUE) %>% 
  gt()
```

Email addresses of non-duke affiliates

```{r}
my_df %>% 
  filter(x1_are_you_affiliated_with_duke_university_duke_medical_center_dcri_or_another_duke_group == "No") %>% 
  select(email, x2_academic_status_or_other, x3_discipline_or_affiliation, x4_institutes_initiatives_or_program_affiliation) %>% 
  gt()
```

Email addresses of non-duke affiliates with duke email addresses. What-the?

```{r}
my_df %>% 
  filter(x1_are_you_affiliated_with_duke_university_duke_medical_center_dcri_or_another_duke_group == "No") %>% 
  select(email, x2_academic_status_or_other, x3_discipline_or_affiliation, x4_institutes_initiatives_or_program_affiliation) %>% 
  filter(str_detect(email, regex("duke", ignore_case = TRUE))) %>% 
  gt()
```

### Institutes

```{r}
my_df %>% 
  count(x4_institutes_initiatives_or_program_affiliation, sort = TRUE) %>% 
  gt()
```

### Advertising source / word-of-mouth 

```{r}
my_df %>% 
  count(x5_where_did_you_hear_about_this_event, sort = TRUE)
```

## CDVS loyalist

```{r}
my_df %>% 
  count(x6_have_you_consulted_with_the_center_for_data_and_visualization_sciences_before_this_workshop, sort = TRUE) %>% 
  gt()
```

### Added to email list?

```{r}
my_df %>% 
  count(x7_would_you_like_to_receive_more_information_about_cdvs_events_and_training) %>% 
  gt()
```

### Survey

```{r}
my_df %>% 
  count(x8_im_interested_in_registering_for_this_workshop_because, sort = TRUE) %>% 
  gt()
```

```{r}
my_df %>% 
  count(x8_im_interested_in_registering_for_this_workshop_because, sort = TRUE) %>% 
  filter(x8_im_interested_in_registering_for_this_workshop_because != "-") %>% 
  separate_rows(x8_im_interested_in_registering_for_this_workshop_because, sep = ",") %>% 
  mutate(x8_im_interested_in_registering_for_this_workshop_because =
           str_trim(x8_im_interested_in_registering_for_this_workshop_because)) %>% 
  ggplot(aes(fct_rev(fct_infreq(x8_im_interested_in_registering_for_this_workshop_because)))) +
  geom_bar() +
  coord_flip()
```


## Create print roster

```{r write-roster, eval=params$generate_print_roster}
example_df <- tibble(
  Attendance = "X",
  last_name = "CHIGURH", 
  first_name = "ANTON", 
  email = "cipher@cloud.net", 
  affiliated = "EXAMPLE",
  status = "EXAMPLE", 
  discipline = "EXAMPLE")


# Create attendance CSV file
workshop_metadata %>% 
  add_row(var = "----", val = "----") %>% 
  write_excel_csv("output/attendance_upload/attendance-roster.csv", col_names = FALSE)

# append the Roster tibble 
write_excel_csv(my_df %>% 
                  mutate(Attendance = "", .before = first_name) %>% 
                  arrange(last_name) %>% 
                  select(last_name, first_name, email,
                         affiliated = x1_are_you_affiliated_with_duke_university_duke_medical_center_dcri_or_another_duke_group, 
                         status = x2_academic_status_or_other, 
                         discipline = x3_discipline_or_affiliation,
                         email_list = x7_would_you_like_to_receive_more_information_about_cdvs_events_and_training) %>% 
                  bind_rows(example_df) %>% 
                  select(Attendance, everything()) %>% 
                  arrange(desc(Attendance)) %>% 
                  mutate(Attendance = if_else(is.na(Attendance), "", Attendance)),
                "output/attendance_upload/attendance-roster.csv", append = TRUE, col_names = TRUE)

```

## Mailing list

```{r email subscribers, eval=params$generate_email_subscribers}
my_df %>% 
  filter(x7_would_you_like_to_receive_more_information_about_cdvs_events_and_training == "Yes") %>% 
  arrange(email) %>% 
  select(email) %>% 
  write_csv("output/email_subscriptions/emails_2_update_lists.csv"  , col_names = FALSE)
```

## Attendance for Google

```{r}
temp_df_names <- attendance_headers %>% 
  select(`First Name`, `Last Name`, Email, `Booking Made`, `Registration Type`, Attendance, ,
         `Are you affiliated with Duke University, Duke Medical Center, DCRI, or another Duke group?`,
         `Academic Status (or other)`, `Discipline or Affiliation`, 
         `Institutes, Initiatives, or Program Affiliation`, `Where did you hear about this event?`,
         `Have you consulted with Data and Visualization Services before this workshop?`,
         `Would you like to receive more information about DVS events and training?`,
         `I'm interested in registering for this workshop because:`,
         `If other, describe below:`,
         `Registration Status (Registered, Waitlist, or Walk-in)`) %>% 
  names()

names(my_df) <- temp_df_names

my_df <- bind_rows(attendance_headers, my_df) 

my_df <- my_df %>% 
  drop_na(Attendance) %>%
  mutate(WorkshopID = registered_df$wid[1]) %>% 
  mutate(`Workshop Date` =  workshop_date$date) %>% 
  mutate(`Workshop Name` = workshop_title) %>% 
  arrange(`Last Name`)
```

```{r upload to google drive, eval=params$upload_googlesheets}
# goog_file_title <- my_df %>% 
#   slice_head(n = 1) %>% 
#   select(`Workshop Name`) %>% 
#   # mutate(`Workshop Name` = str_remove_all(`Workshop Name`, "[:symbol:]|[:punct:]")) %>% 
#   pull(`Workshop Name`)
# goog_file_title

googlesheets4::gs4_create(workshop_title, sheets = my_df)
```



