---
title: "Workshop Attendees"
subtitle: "Produce Roster for printing via Excel ; Visualize Attendance"
output: 
  html_document:
    fig_width: 10
    fig_height: 7
    fig_caption: true
    dev: "svg"
date: "`r Sys.Date()`"
params:
  upload_googlesheets: FALSE  # if you want to upload to google, change this option to TRUE or see https://rmarkdown.rstudio.com/lesson-6.html  ## See more on INTERACTIVE parameters: https://bookdown.org/yihui/rmarkdown/params-knit.html#the-interactive-user-interface
---

Run this as an attendance roster file generator, at the R console:


```r
rmarkdown::render("libcal_roster.Rmd", output_file = 
    paste("outfile/roster_summary", Sys.Date(), sep="_"))
```

Alternatively, run this to **upload as a googleSheet**

```
# for upload to Google Drive
rmarkdown::render("libcal_roster.Rmd", params = list(upload_googlesheets = "TRUE"))
```


## Load Packages

```{r packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(fs)
library(viridis)
library(knitr)
library(kableExtra)
library(lubridate)
library(googledrive)
```

## Functions

```{r}
waitlist_fix = function(var1) {
  str_replace(var1, "wait_list", "waitlist")
}

extract_toTitle = function(var1, word_set) {
  str_to_title(str_extract(var1, word_set))
}

registered_translation = function(var1, word1, newword) {
  mutate(var1 = if_else(var1 == word1, word1, newword))
}
```


## Import Data

### Registration Data

Instructor will download the registered and waitlist files from libcal (SpringShare).  Below, the instructor will choose the location of these files on the filesystem.  

```{r import-registration-data, message=FALSE, warning=FALSE}
# files_table <- tibble(path_rel(choose.files()))
files_table <- tibble(path_rel(choose.files())) %>% 
  rename(relpath = 1)

full_file_names <- files_table %>% 
#  rename(relpath = value) %>% 
  filter(str_detect(path_ext(relpath), 
                    fixed("csv", ignore_case = TRUE))) %>% 
  mutate(reg_data = 
           map(relpath, read_csv, skip = 8)) %>%  # jrl was 9
  unnest()
```

### Workshop Metadata

```{r roster-header, message=FALSE, warning=FALSE}
attendees_header <- read_csv(head(files_table$relpath, 1), 
                              skip=1, n_max = 6, 
                              col_names = FALSE) 
```


## Write Roster

First, make example record

```{r anton}
example <- tibble(
  Attendance = "X",
  `Last Name` = "CHIGURH", 
  `First Name` = "ANTON", 
  #Attendance = "X",
  Email = "cipher@cloud.net", 
  Status = "EXAMPLE", 
  Discipline = "EXAMPLE", 
  Registration = "EXAMPLE")

```

Prepare and Wrangle Roster tibble for print-to-outfile via post-process printing/formatting via Excel

```{r}
# jrl rename colnames b/c shpringshare changed var format late 2019
colnames(full_file_names) <- full_file_names %>% 
  colnames() %>% 
  str_replace_all("^\\d{1,2}\\s", "")

roster <- full_file_names %>% 
  select(`Last Name`, `First Name`, `Email`, 
         Status = `Academic Status (or other)`, 
         Discipline = `Discipline or Affiliation`,
         relpath) %>% 
  mutate(relpath = waitlist_fix(relpath)) %>% 
  mutate(Registration = extract_toTitle(relpath, "(attendees|waitlist)")) %>% 
  mutate(Registration = if_else(
    Registration == "Attendees", "Registered", Registration)) %>% 
  select(-relpath) %>% 
  arrange(`Last Name`) 
```


Combine Roster with Example record

```{r}
roster <- bind_rows(example, roster) 
roster$Attendance <- replace_na(roster$Attendance, " ")
```

### Write/Export CSV File 

... for import into Excel because the formatting printing just seems nicer, albeit manual.  In excel, I use the **format tables** option to format the roster.  I also **print options** to set **landscape orientation** and **scale to fit all columns** on one page.

I could use `knitr::kable()` to print this out here, but this is a rare instance where I prefer the Microsoft approach.  Feel free to develop that if you like.

```{r write-roster}
# Create attendance CSV file
attendees_header %>% 
  write_excel_csv("outfile/attendance-roster.csv", col_names = FALSE)

# append blank line to attendance CSV file
write_excel_csv(tibble(" "), "outfile/attendance-roster.csv", append = TRUE)

# append the Roster tibble 
write_excel_csv(roster, "outfile/attendance-roster.csv", append = TRUE, col_names = TRUE)

```


## Visualize Attedance

```{r echo=FALSE}
knitr::kable(attendees_header %>% rename(" " = X1, "  " = X2)) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) 
```


```{r wrangle data, include=FALSE}
roster2 <- full_file_names %>% 
  rename(status = `Academic Status (or other)`) %>% 
  rename(patron = `Have you consulted with the Center for Data and Visualization Sciences before this workshop?`) %>% 
  rename(advertizing_source = 'Where did you hear about this event?') %>% 
  rename(affiliate = "Are you affiliated with Duke University, Duke Medical Center, DCRI, or another Duke group?") %>% 
  rename(interest = "I'm interested in registering for this workshop because:") %>% 
  rename(discipline = `Discipline or Affiliation`) %>% 
  filter(status != "Perpetual") %>% 
  mutate(discipline = case_when(
    discipline == "African and African American Studies" ~ "Afr",
    discipline == "Art, Art History, and Visual Studies" ~ "Art",
    discipline == "Asian and Middle Eastern Studies" ~ "Asia",
    discipline == "Biology" ~ "Bio",
    discipline == "Center for Documentary Studies" ~ "Document",
    discipline == "Chemistry" ~ "Chem",
    discipline == "Classical Studies" ~ "Classics",
    discipline == "Computer Science" ~ "CS",
    discipline == "Cultural Anthropology" ~ "Anthro", 
    discipline == "Dance" ~ "Dance",
    discipline == "Divinity School" ~ "Div",
    discipline == "Duke University Health System (DUHS)" ~ "DUHS",
    discipline == "Economics" ~ "Econ",
    discipline == "Education (Program in Education)" ~ "Edu",
    discipline == "Engineering (Pratt School of Engineering)" ~ "Engr",
    discipline == "English" ~ "Engl",
    discipline == "Evolutionary Anthropology" ~ "Evol-Antro",
    discipline == "Fuqua School of Business" ~ "Fuqua",
    discipline == "Gender, Sexuality, and Feminist Studies" ~ "Gender",
    discipline == "Germanic Languages and Literature" ~ "German",
    discipline == "Graduate Liberal Studies" ~ "Liberal",
    discipline == "History" ~ "Hist",
    discipline == "International Comparative Studies" ~ "Comparative Lit",
    discipline == "Law School" ~ "Law",
    discipline == "Linquistics" ~ "Linquistics",
    discipline == "Literature" ~ "Lit", 
    discipline == "Masters in Interdisciplinary Data Science" ~ "DS",
    discipline == "Mathematics" ~ "Math",
    discipline == "Music" ~ "Music",
    discipline == "Neuroscience" ~ "Neuroscience",
    discipline == "Nicholas School of the Environment" ~ "Nicholas",
    discipline == "Philosophy" ~ "Phil",
    discipline == "Physics" ~ "Physics",
    discipline == "Political Science" ~ "Poli Sci",
    discipline == "Population Health Sciences"~ "Health Sci",
    discipline == "Psychology and Neuroscience" ~ "Psych/Neuro",
    discipline == "Religious Studies" ~ "Relgion",
    discipline == "Romance Studies" ~ "Romance",
    discipline == "Sanford School of Public Policy" ~ "Sanford",
    discipline == "Slavic and Eurasian Studies" ~ "Slavic",
    discipline == "School of Medicine" ~ "Medicine",
    discipline == "School of Nursing" ~ "Nursing",
    discipline == "Sociology" ~ "Sociology",
    discipline == "Statistical Science" ~ "Stats",
    discipline == "Theatre Studies" ~ "Theater",
    discipline == "Other / None" ~ "Other"
    )) %>% 
  mutate(status = fct_infreq(status, ordered = TRUE) ) %>% 
  mutate(discipline = fct_infreq(discipline, ordered = TRUE))
```

```{r wrangle interest inventory, include=FALSE}
interest_inventory <- roster2 %>% 
  mutate(id = paste(`Last Name`, `First Name`, sep = "_")) %>% 
  select(id, status, discipline, interest) %>% 
  mutate(interest = na_if(interest, "-")) %>% 
  separate_rows(interest, sep = ",") %>% 
  mutate(interest = trimws(interest)) %>% 
  drop_na(interest) %>%   
  mutate(interest = case_when(
    interest == "I believe this topic is important for my career goals" ~ "Career",
    interest == "This topic is directly relevant to a course or project I'm pursuing" ~ "Course/Project",
    interest == "I am generally curious about the topic" ~ "Curious",
    interest == "I have enjoyed past DVS workshops" ~ "Loyalist",
    interest == "Other" ~ "Other"
  )) %>% 
  mutate(interest = fct_infreq(interest, ordered = TRUE))
```

```{r echo=FALSE}
ggplot(roster2) +
  geom_bar(aes(x = fct_rev(status), 
               fill = fct_rev(patron)),
           color = "black") +
  scale_fill_viridis(discrete = TRUE) +
  coord_flip() +
  labs(y = "",
       x = "Status",
       title = "DVS Patron Status",
       fill = "Patron")
```


```{r dev='svg', echo=FALSE}
roster2 %>% 
  mutate(discipline = fct_lump(discipline, n = 9)) %>% 
  ggplot() +
  geom_bar(aes(x = fct_rev(discipline), 
               fill = fct_rev(status)),
           color = "black") +
  coord_flip() +
  theme(axis.text.y = element_text(angle = 45),
        axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  guides(fill=guide_legend(title="Status")) +
  labs(title = "Attendance by Discipline")
  
```
```
{r}
ggsave("who_we_are.svg")
```

```
{r}
library(hrbrthemes)
hrbrthemes::import_roboto_condensed()
```


```
{r echo=FALSE, message=FALSE, warning=FALSE, dev='svg'}
roster2 %>% 
  mutate(discipline = fct_lump(discipline, n = 9)) %>% 
  ggplot() +
  geom_bar(aes(x = fct_rev(discipline), 
               fill = fct_rev(status))) +
  coord_flip() +
  scale_fill_ipsum() +
  theme_ipsum(grid = "X") +
  theme(#axis.text.y = element_text(angle = 45),
        plot.title.position = "plot") +
  guides(fill=guide_legend(title="Status", 
                           reverse = TRUE)) +
  labs(title = "Attendance by Discipline",
       subtitle = "CDVS Workshop: quickStart R Part 1",
       caption = "Source: CDVS Workshop Registration",
       x = "", y = "")
ggsave("who_we_are.svg")
```


```
{r echo=FALSE, fig.height=8, message=FALSE, warning=FALSE, dev='svg'}
roster2 %>% 
  mutate(discipline = fct_lump(discipline, n = 9)) %>% 
  ggplot() +
  geom_bar(aes(x = fct_rev(discipline), 
               fill = fct_rev(discipline)),
           show.legend = FALSE) +
  facet_wrap(~ status) +
  coord_flip() +
  scale_fill_ipsum() +
  theme_ipsum(grid = "X") +
  theme(#axis.text.y = element_text(angle = 45),
        plot.title.position = "plot") +
  guides(fill=guide_legend(title="Status")) +
  labs(title = "Attendance by Discipline",
       subtitle = "CDVS Workshop: quickStart R Part 1",
       caption = "Source: CDVS Workshop Registration",
       x = "", y = "")

ggsave("who_we_are_facet.svg")
```


```{r echo=FALSE}
interest_inventory %>% 
  ggplot() +
  geom_bar(aes(x = fct_rev(interest), 
               fill = fct_rev(status)),
           color = "black") +
  coord_flip() +
  labs(y = "",
       x = "Interest",
       title = "DVS Patron Interest Questionnaire",
       fill = "Status")
```


```{r echo=FALSE}
interest_inventory %>% 
  ggplot() +
  geom_bar(aes(fct_rev(fct_lump(fct_infreq(discipline), prop = 0.02)),
               fill = fct_rev(interest)),
           color = "black") +
  coord_flip() +
  labs(y = "",
       x = "Discipline",
       title = "Questionnaire by Discipline",
       fill = "Interest")
```


## Upload to Google Drive

Wrangle the content and order of the Tibble variables

```{r}
for_goog <- full_file_names %>% 
  mutate("Workshop Name" = attendees_header %>% spread(X1, X2) %>% select(Event) %>% toString()) %>% 
  mutate("Workshop Date" = attendees_header %>% 
           spread(X1, X2) %>% 
           select(`Date & Time`) %>% 
           str_replace("^\\d+.*pm,\\s", "") %>% 
           mdy()) %>%   # jrl fix date grab b/c springshare changed format
  mutate(`Attended (x or blank)` = " ") %>% 
  mutate(relpath = waitlist_fix(relpath)) %>% 
  mutate(`Registration Status (Registered, Waitlist, or Walk-in)` = extract_toTitle(relpath, "(attendees|waitlist)")) %>% 
  mutate(`Registration Status (Registered, Waitlist, or Walk-in)` =
           if_else(`Registration Status (Registered, Waitlist, or Walk-in)` == "Attendees", 
                   "Registered", 
                   `Registration Status (Registered, Waitlist, or Walk-in)`)) %>% 
  mutate(metadata_filename = str_extract(relpath, "lc_\\w+_\\d+")) %>%
  separate(metadata_filename, into = c("prefix", "type", "WorkshopID", "pid")) %>% 
  #separate(workshop_id, into = c("WorkshopID", "pid"), sep = 8) %>%
  #mutate(WorkshopID = "999999") %>% 
  rename(`Booking Made` = `Booking made`) %>% 
  mutate(Attendance = "") %>% 
  select(-relpath, -prefix, -type, -pid) %>% 
  arrange(`Last Name`) %>% 
  select(17, 18, 16, 15, 19, everything())
```

Upload to Google as a googlesheet.  First time through, run this manually, look in the console to answer the .httr_auth

```{r upload_to_googledrive, eval=params$upload_googlesheets}
sheetname <- paste(for_goog$`Workshop Name`[1], for_goog$`Workshop Date`[1], sep = "_")
local_filename <- str_remove_all(sheetname, "[^a-zA-Z0-9]")
local_filename <- path_ext_set(local_filename, "csv")

write_csv(for_goog, path("data", local_filename))

drive_upload(path("data", local_filename), name = sheetname, type = "spreadsheet")
```


## email list as .csv -- to paste into dvs-announce list

```{r build-and-write-dvsannounce-list}
roster2%>% 
  filter(`Would you like to receive more information about CDVS events and training?` == "Yes") %>% 
  select(Email) %>% 
  arrange(Email) %>% 
  write_delim("outfile/dvs-announce_append-email.txt", col_names = FALSE)
```




